\section{Introduction}
\label{sec:intro}

Läderach is a Swiss premium chocolate manufacturer with its origins in the Canton
of Glarus. The company was founded in 1962 by chocolatier Rudolf Läderach Jr. in
Glarus and developed from a small chocolate factory into an internationally active
brand for high-quality Swiss chocolate \cite{laderachMilestones}. In its early
years, Läderach mainly operated as a specialist supplier for selected Swiss
confectioners. Only later did the company become more visible as a consumer brand
in its own right. An important step in this development was its entry into direct
retail, particularly through the acquisition of Merkur stores in 2004
\cite{laderachMilestones}. As a result, Läderach increasingly shifted from being
primarily a production and supplier business to becoming an integrated premium
provider with its own boutiques and direct contact with customers.

To this day, Läderach remains a fully family-owned company. Its ownership and
management tradition across several generations strongly shapes the identity of
the brand. After the founding generation, Jürg Läderach took over operational
leadership, before the third generation assumed central management roles from
2018 onwards, with Johannes Läderach as CEO and Elias Läderach as Chief Creative
Officer \cite{laderachLeadershipNextGeneration,laderachMilestones}. This
continuity is an important element of the company’s brand identity, because
Läderach does not only sell chocolate, but also emphasises values such as
craftsmanship, Swiss origin, freshness, and quality.

The company positions itself in the premium segment of the chocolate and
confectionery industry. Läderach produces its chocolate in Switzerland and
particularly emphasises its control over the value chain: from the selection and
processing of raw materials to the presentation of products in its own
chocolateries \cite{laderachOfficialWebsite,laderachOurBusinessUnits}. This
vertical integration supports the company’s claim to produce chocolate at the
highest level. Läderach is especially known for fresh chocolate creations such as
FrischSchoggi, pralines, truffles, and seasonal specialities. The brand combines
traditional Swiss confectionery craftsmanship with innovation; one visible
example is Elias Läderach, who became the first Swiss person to win the title of
World Chocolate Master in 2018 \cite{laderachMilestones}.

Compared with major Swiss chocolate groups such as Lindt \& Sprüngli, Läderach is
significantly smaller. However, within the premium chocolate segment, the company
has grown considerably. Today, Läderach operates more than 250 chocolateries in
over 30 countries and employs more than 2,500 people from over 80 nationalities
\cite{laderachOfficialWebsite}. These figures show that Läderach is no longer
only a regional family business, but an internationally present provider of Swiss
premium chocolate. At the same time, the brand remains closely connected to its
origins in the Canton of Glarus and to its ambition to produce fresh,
high-quality chocolate in Switzerland. Läderach is therefore a relevant example
of a family-owned company that has expanded strongly while maintaining its
positioning as a specialised premium producer.

\subsection{Current Leadership}

Läderach remains a fully family-owned company and is now led by the third
generation of the Läderach family. The company states that it is still 100\%
family-owned; however, as it is privately held, there is no public shareholder
register or detailed information on how ownership is divided among individual
family members. This makes the exact ownership structure difficult to assess from
publicly available sources.

Operationally, the third generation plays a central role in the company’s current
leadership. Johannes Läderach serves as CEO and Chairman of the Board, while
Elias Läderach is Vice Chairman of the Board and is strongly associated with the
company’s product and creative development. David Läderach is also involved in
the leadership structure as a board member and Managing Director for Germany.
Together, they represent the continuation of family control within the company’s
governance and management. Läderach’s current leadership structure therefore
shows a strong continuity between ownership, strategic decision-making, and
family identity.

\subsection{Resource Sourcing and Supply Chain}

Läderach’s premium positioning is closely connected to the origin and quality of
its raw materials. The company emphasises a ``bean-to-bar'' responsibility, which
means that it aims to control important stages of the chocolate value chain, from
the sourcing of cocoa beans to production and retail distribution. Its cocoa is
sourced from several origin countries, including Ghana, Madagascar, Brazil,
Ecuador, Nicaragua, Costa Rica, and India. This variety of sourcing countries
allows Läderach to work with different cocoa profiles and supports its image as a
producer of high-quality, origin-focused chocolate.

At the same time, Läderach strengthens its Swiss premium identity through the
sourcing of key ingredients from Switzerland. Milk and sugar are sourced
domestically, which reinforces the company’s claim that its chocolate is strongly
rooted in Swiss production and quality standards. For nuts, the company highlights
Piedmont hazelnuts from Italy, which are widely associated with premium
confectionery and help support the luxury image of the brand.

However, compared with larger competitors such as Lindt \& Sprüngli, Läderach
publishes relatively limited information about its supplier network and sourcing
transparency. Lindt operates a much larger and more industrialised global sourcing
system and invests heavily in traceability, sustainability programmes, and
large-scale ESG initiatives. Läderach, by contrast, appears to rely on a smaller
and more specialised premium sourcing network, which may allow closer
relationships with selected suppliers but provides less publicly available detail
on the overall structure of its supply chain.

Both Läderach and Lindt are affected by broader challenges in the cocoa supply
chain. Droughts, climate change, cocoa diseases in West Africa, yield insecurity,
and rising cocoa prices create pressure on chocolate manufacturers. For Läderach,
these challenges are especially relevant because the company’s brand depends
strongly on consistent quality, freshness, and premium raw materials. Resource
price volatility and supply insecurity therefore represent important governance
and strategic risks for the company.