\section{Company Overview}

Läderach is a Swiss premium chocolate manufacturer and retailer operating internationally through its own boutiques and franchise network.

Official website:
\begin{itemize}
    \item \cite{laderachOfficialWebsite}
\end{itemize}

\section{Legal Structure}

The main operating entity is:

\begin{itemize}
    \item \textbf{Läderach (Schweiz) AG}
\end{itemize}

The legal form is an \textbf{Aktiengesellschaft (AG)} under Swiss law.

Registered address:
\begin{itemize}
    \item Bleiche 14, 8755 Ennenda, Switzerland
\end{itemize}

The commercial register describes the company purpose as the manufacture and sale of chocolate, confectionery, and bakery products.

\subsection*{Sources}

\begin{itemize}
    \item \cite{moneyhouseLaederachSchweizAG}
\end{itemize}

\section{Ownership and Shareholders}

Läderach describes itself as a:

\begin{quote}
``100\% family-owned company.''
\end{quote}

The Läderach family controls the business.

Publicly identified family members involved in ownership and management include:

\begin{itemize}
    \item Johannes Läderach
    \item Elias Läderach
    \item David Läderach
\end{itemize}

\subsection*{Important limitation}

The company is privately held. No public shareholder register or detailed ownership percentages could be independently verified.

\subsection*{Sources}

\begin{itemize}
    \item \cite{laderachLeadershipNextGeneration}
\end{itemize}

\section{Management and Board of Directors}

\subsection{Executive Management}

Publicly identified executives include:

\begin{itemize}
    \item Johannes Läderach --- CEO and Chairman of the Board
    \item Elias Läderach --- Vice Chairman of the Board
    \item David Läderach --- Board member and Managing Director Germany
\end{itemize}

Additional executives identified in business databases include:

\begin{itemize}
    \item Luc Van den Bossche --- COO
    \item Markus Huber --- CFO / Head Global IT \& Corporate Services
\end{itemize}

\subsection*{Sources}

\begin{itemize}
    \item \cite{wikipediaLaederach}
    \item \cite{laderachLeadershipNextGeneration}
    \item \cite{leadiqLaederach}
\end{itemize}

\subsection{Board of Directors}

Publicly identified board members include:

\begin{itemize}
    \item Johannes Läderach
    \item Elias Läderach
    \item David Läderach
    \item Cornelia Ritz Bossicard
    \item Andreas Pfluger
    \item Walter Huber
\end{itemize}

\subsection{Notable Board Members}

\begin{itemize}
    \item \textbf{Cornelia Ritz Bossicard}: associated with the Migros Board and ETH Board.
    \item \textbf{Andreas Pfluger}: former executive board member at Lindt \& Sprüngli.
    \item \textbf{Walter Huber}: former executive at Migros Group.
\end{itemize}

\subsection*{Sources}

\begin{itemize}
    \item \cite{laderachLeadershipNextGeneration}
    \item \cite{lindtSpruengliOfficial}
\end{itemize}

\section{Industry and Business Activities}

Läderach operates in the following sectors:

\begin{itemize}
    \item Premium chocolate manufacturing
    \item Confectionery
    \item Luxury food products
    \item Retail chocolate boutiques
\end{itemize}

The company emphasizes a vertically integrated ``bean to bar to you'' model.

Business units include:

\begin{itemize}
    \item Retail
    \item Production
    \item Supply chain management
    \item Corporate services
\end{itemize}

\subsection*{Sources}

\begin{itemize}
    \item \cite{wikipediaLaederach}
    \item \cite{laderachOurBusinessUnits}
\end{itemize}

\section{Headquarters}

The headquarters are located in:

\begin{itemize}
    \item Ennenda, Canton of Glarus, Switzerland
\end{itemize}

Operational infrastructure is concentrated in Ennenda and Bilten.

\subsection*{Sources}

\begin{itemize}
    \item \cite{leadiqLaederach}
    \item \cite{wikipediaLaederach}
\end{itemize}

\section{Production Locations}

Läderach states that all chocolate production is carried out in Switzerland.

Main production locations:

\begin{itemize}
    \item Ennenda, Switzerland
    \item Bilten, Switzerland
\end{itemize}

\subsection{Production Facilities}

\begin{itemize}
    \item A major chocolate mass production facility opened in Bilten in 2012.
    \item A second Bilten factory reportedly entered production in 2025.
    \item The former German production site in Dillenburg was closed in 2019.
\end{itemize}

\subsection{Production Capacity}

The Bilten facility reportedly had an annual capacity of approximately:

\begin{itemize}
    \item 1,100 tons per year (2012 figure)
\end{itemize}

\subsection*{Important limitation}

No reliable public source for current total annual production volume could be identified.

\subsection*{Sources}

\begin{itemize}
    \item \cite{laderachBestManaged2024}
    \item \cite{wikipediaLaederach}
\end{itemize}

\section{Retail Network}

\subsection{Number of Stores}

Public figures vary by year:

\begin{itemize}
    \item 140 boutiques in 16 countries (2021)
    \item Over 200 chocolateries worldwide (2024)
    \item Approximately 220 stores worldwide (2025 references)
\end{itemize}

The company announced the opening of its 200th chocolaterie in London in 2024.

\subsection*{Sources}

\begin{itemize}
    \item \cite{laderachLeadershipNextGeneration}
    \item \cite{laderachOurBusinessUnits}
    \item \cite{laderachPressReleasesUK}
    \item \cite{wikipediaLaederach}
\end{itemize}

\subsection{Countries of Operation}

Countries mentioned in public sources include:

\begin{itemize}
    \item Switzerland
    \item Germany
    \item Austria
    \item United Kingdom
    \item France
    \item United States
    \item Canada
    \item South Korea
    \item India
    \item Malaysia
    \item Middle Eastern franchise markets
\end{itemize}

Reported geographical scope varies between 16 and 20 countries depending on the source and year.

\subsection*{Important limitation}

The exact current number of operating countries could not be conclusively verified.

\subsection*{Sources}

\begin{itemize}
    \item \cite{wikipediaLaederach}
    \item \cite{laderachLeadershipNextGeneration}
    \item \cite{deloitteBestManagedCompanies}
\end{itemize}

\section{Revenue and Financial Figures}

Reliable financial data is limited because Läderach is privately held.

Publicly available figures include:

\begin{itemize}
    \item Approximate revenue of CHF 120 million (2016 figure)
    \item Turnover growth of +14\% during January--October 2024
    \item Forecasted full-year growth above 15\% for 2024
\end{itemize}

Commercial databases estimate annual revenue around USD 103 million.

\subsection*{Important limitation}

No recent audited consolidated financial statements were identified publicly.

\subsection*{Sources}

\begin{itemize}
    \item \cite{wikipediaLaederach}
    \item \cite{laderach200thChocolaterie2024}
    \item \cite{prospeoLaederachRevenue}
\end{itemize}

\section{Employees}

Reported employee figures include:

\begin{itemize}
    \item Approximately 750 employees (2015)
    \item More than 1,300 employees (2021)
    \item Approximately 2,000--2,100 employees globally (2024--2025)
\end{itemize}

Reported workforce diversity:

\begin{itemize}
    \item More than 50 nationalities (2021)
    \item Around 70 nationalities (2024)
\end{itemize}

\subsection*{Sources}

\begin{itemize}
    \item \cite{wikipediaLaederach}
    \item \cite{laderachLeadershipNextGeneration}
    \item \cite{hrCampusLaederachSwitzerland}
    \item \cite{laderachBestManaged2024}
\end{itemize}

\section{Other Interesting Figures and Facts}

\subsection{Vertical Integration}

Läderach controls:

\begin{itemize}
    \item Cocoa sourcing
    \item Chocolate mass production
    \item Product manufacturing
    \item Retail distribution
\end{itemize}

The company states that chocolate mass production is conducted internally.

\subsection*{Sources}

\begin{itemize}
    \item \cite{laderachOurBusinessUnits}
    \item \cite{laderachLeadershipNextGeneration}
\end{itemize}

\subsection{Cocoa Sourcing Countries}

Public sources identify cocoa sourcing partnerships in:

\begin{itemize}
    \item Madagascar
    \item Costa Rica
    \item Trinidad
    \item Ghana
    \item Brazil
    \item Ecuador
\end{itemize}

\subsection*{Sources}

\begin{itemize}
    \item \cite{wikipediaLaederach}
    \item \cite{laderachHerkunft}
\end{itemize}

\subsection{International Expansion Milestones}

Notable milestones include:

\begin{itemize}
    \item 100th store opened on Fifth Avenue, New York (2020)
    \item 200th store opened in London (2024)
\end{itemize}

\subsection*{Sources}

\begin{itemize}
    \item \cite{laderachPressReleasesUK}
\end{itemize}

\section{Controversies and Reputational Issues}

Public reporting has connected former company leader Jürg Läderach with conservative Christian organizations and controversies surrounding affiliated educational institutions.

Swiss media reported reputational effects on the brand.

\subsection*{Important note}

These issues appear separate from the company's commercial operations but have received significant media attention.

\subsection*{Sources}

\begin{itemize}
    \item \cite{swissinfoLaederachScandal}
\end{itemize}

\section{Summary Table}

\begin{longtable}{>{\raggedright\arraybackslash}p{5cm} >{\raggedright\arraybackslash}p{9cm}}
\toprule
\textbf{Topic} & \textbf{Information} \\
\midrule
Legal form & Läderach (Schweiz) AG \\
Ownership & 100\% family-owned \\
Headquarters & Ennenda, Glarus, Switzerland \\
Industry & Premium chocolate and confectionery \\
CEO & Johannes Läderach \\
Production & Switzerland only \\
Stores & Approximately 200--220 worldwide \\
Countries & Approximately 16--20 countries \\
Employees & Approximately 2,000+ \\
Revenue & Private; historical CHF 120 million reference \\
Production capacity & At least 1,100 tons/year at Bilten facility \\
\bottomrule
\end{longtable}
